\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-27 metatheory-condensed.tex
Comments on Linkage achieves code reuse Linkage Transformer is only a library function.

\ruleref{lkg/proj} indicates how linkage captures the idea of \textit{code reuse}, as $\lkgproj{2}{-}$ will lead to the boxed term that is parametric on the surrounding linkage $\lsigprojT{\lsig}$ . To code reuse, we simply project out a field from the parent and add back to the children family.
\newpage 
Adding new types into signature \ruleref{Sig Add} requires a \textit{sealing judgement} $\goodSeal{\Gamma}{f}{\sigma}{A}$, which is an alias of a term judgement. Sealing is corresponding \textit{to indicating whether each field is overridable(extensible) or non-overridable (thus definitionally exposed) in the Coq Plugin}. 
Concretely, we encode our STLC example to show the motivation of the sealing.
%\YZ{Is sealing used only for late-binding the signatures of inductive types? Do I understand correctly that late binding of other kinds of fields (like subst) is achieved by the boxed premise in rule "LNKG ADD"?}\EDJreply{All late-bound are achieved by ``selective-abstraction'' imposed by sealing. For example, recursion will be consequently abstracted because of the abstraction of the inductive type it recurse on. 
%}\EDJreply{Sorry, I see what you mean. Yes. the box part is important for late-binding. But the functionality of sealing is always there. They are both required to achieve overriding. A illustrative example is, if the type is $S(\bot)$, then even with the boxed premise, it is still not overridable because the type itself restricts all the possibilities.}\YZreply{
%  By "selective abstraction", do you mean in the metatheory the programmer chooses what and how to abstract?
%}\EDJreply{Yes.}

@@

However, in the plugin implementation, we use "Family"s to organize the code reuse. They are second class objects like Coq's "Module". What's more, a "Family" (with or without "extends" clause) can be considered as a standalone piece of code trying to \textit{inherit} an existent (but maybe empty) family. Thus we model them using \textit{inheritance judgement} $\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}$ instead of considering them as first class terms. The only way to use $h$ is by \ruleref{Inh} and transforming a linkage of signature $\sigma_1$ to another linkage of $\sigma_2$. Inheritance judgement can be inductively constructed via inheriting operations, overriding operations, extending operations and etc, corresponding to "Inherit", "Override" and "Extend" command  in our plugin implementation.

>>>>

\ruleref{lkg/proj} indicates how linkage captures the idea of \textit{code reuse}, as $\lkgproj{2}{-}$ will lead to the boxed term that is parametric on the abstracted interface of linkage $\lsigprojT{\lsig}$ . To code reuse, we simply project out a field from the parent and add back to the children family.
\newpage 
Adding new types into signature \ruleref{Sig Add} requires a \textit{sealing judgement} $\goodSeal{\Gamma}{f}{\sigma}{A}$, which is an alias of a term judgement. Sealing is corresponding \textit{to indicating whether each field is overridable(extensible) or non-overridable (thus definitionally exposed) in the Coq Plugin}. 
Concretely, we encode our STLC example to show the motivation of the sealing.
%\YZ{Is sealing used only for late-binding the signatures of inductive types? Do I understand correctly that late binding of other kinds of fields (like subst) is achieved by the boxed premise in rule "LNKG ADD"?}\EDJreply{All late-bound are achieved by ``selective-abstraction'' imposed by sealing. For example, recursion will be consequently abstracted because of the abstraction of the inductive type it recurse on. 
%}\EDJreply{Sorry, I see what you mean. Yes. the box part is important for late-binding. But the functionality of sealing is always there. They are both required to achieve overriding. A illustrative example is, if the type is $S(\bot)$, then even with the boxed premise, it is still not overridable because the type itself restricts all the possibilities.}\YZreply{
%  By "selective abstraction", do you mean in the metatheory the programmer chooses what and how to abstract?
%}\EDJreply{Yes.}

@@

However, in the plugin implementation, we use "Family"s to organize the code reuse. They are second class objects like Coq's "Module". What's more, a "Family" (with or without "extends" clause) can be considered as a standalone piece of code trying to \textit{inherit} an existent (but maybe empty) family. Thus we model them using \textit{inheritance judgement} $\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}$ instead of considering them as first class terms. Inheritance judgement is like ``library function'' upon linkage for achieving inheritance and overriding. The only way to use $h$ is by \ruleref{Inh} and transforming a linkage of signature $\sigma_1$ to another linkage of $\sigma_2$. Inheritance judgement can be inductively constructed via inheriting operations, overriding operations, extending operations and etc, corresponding to "Inherit", "Override" and "Extend" command  in our plugin implementation.
